### 2025-04-09 analysis/analysis.qmd
rendered the html versions

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
print(funnel(m.cor.c.all, common = FALSE, studlab=TRUE,backtransf=TRUE))

@@

#### Custom plot

```{r}
tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)

tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
tmpdata$citekey<-factor(tmpdata$citekey)

g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
  geom_point(show.legend = FALSE) +
  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
  ylab('Standard Error') + 
  xlab('r')+
  scale_y_reverse()+
#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
#  coord_flip()+
  theme_bw()
print(g)
```

>>>>

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
#print(funnel(m.cor.c.all, common = FALSE, studlab=TRUE,backtransf=TRUE))

@@
